Model Establishment for WMT Stock

### 2017-06-15 code/Section 3 AMZN Stock(revised).Rmd
Update Code for Section 3 AMZN & WMT Stock

m1 = garchFit(~1 + garch(1,0), data = lgreturn/100,trace=F) # Fit an ARCH(1) model
summary(m1)

m2 = garchFit(~1 + garch(1,1), data = lgreturn/100,trace=F) # Fit a GARCH(1,1) model
summary(m2)

@@

## Predict
```{r, echo=TRUE, message=FALSE, warning=FALSE}
sigma2=predict(m2,50)
print(sigma2)
library(sciplot)
plot(sigma2$meanForecast,ylim=c(-0.05,0.05))
lines(c(1:50),sigma2$meanForecast+1.96*sigma2$meanError,col='blue')
lines(c(1:50),sigma2$meanForecast-1.96*sigma2$meanError,col='blue')
```

>>>>

m1 = garchFit(~ garch(1,0), data = lgreturn, cond.dist = "norm") # Fit an ARCH(1) model
summary(m1)

m2 = garchFit(~ garch(1,1), data = lgreturn, cond.dist = "norm") # Fit a GARCH(1,1) model
summary(m2)

@@

### 2017-06-15 code/Section 3 WMT Stock(revised).Rmd
Update Code for Section 3 AMZN & WMT Stock

---
title: "Model Establishment for AMZN Stock"
author: "group project"
date: "2017-06-13"
output: html_document
---

@@

## Testing ARCH Effects
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(TSA)
library(xts)
library(xtable)
library(lubridate)
library(readxl)
AMZN <- read_excel("F:/CUEB/Junior/SPRING/FDA/FDA_project_group_XN/data/AMZN.xlsx",col_types = c("date", "numeric", "numeric", "numeric", "numeric", "numeric"))
AMZN = AMZN[-1763:-1764,]
lgreturn = diff(log(AMZN$close))*100

>>>>

---
title: "Model Establishment for WMT Stock"
author: "group project"
date: "2017-06-15"
output: html_document
---

@@

## Testing ARCH Effects
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(TSA)
library(xts)
library(xtable)
library(lubridate)
library(readxl)
WMT <- read_excel("F:/CUEB/Junior/SPRING/FDA/FDA_project_group_XN/data/WMT.xlsx",col_types = c("date", "numeric", "numeric", "numeric", "numeric", "numeric"))
WMT = WMT[-1763:-1764,]
lgreturn = diff(log(WMT$close))*100
